---
title: "ctapply - An R package to measure central tendency and spread"
author: "Anthony McCofie - anthonymccofie@usf.edu"
date: "April 23, 2022"
output:
  pdf_document: 
    number_sections: true
---

ctapply: **Object Summaries**

**Description:**

**ctapply** is a package used to produce summaries of basic statistics, such as central tendency(mean, median..) and standard deviation (spread). 
The package calls specific methods to produce the result.  The user have option to print the result.


The sample data used for this package is: **Cost Function of Electricity Producers (1955)**

Below are the fields for the sample data used for the package
```{r echo=FALSE}
library(ctapply)
head(electricdata)
```

**Usage:**

* You can use the package in two ways:
  + Either with the data that comes with the package **electricdata** as shown below  
  ```{r setup, warning=FALSE, message=FALSE}
  ctapply(electricdata$fuel, options=2)
  ctpairplot(electricdata)
  ```
  + Or use your own data such as creating a numeric vector shown below:
  ```{r warning=FALSE, message=FALSE}
  data1 <- c(4,5,6,5,6,5,6,4,6,5,6,4,5,4,5,6)
  ctapply(data1, options=2)
  cthistgraph(electricdata$cost)
  ```
\newpage

**Arguments**

**object**    : An object for which a summary is desired. This could be a numeric vector or a data frame dataset.

**np**        : A boolean value **(TRUE/FALSE)**.  The statistics to use **(Mean, Median,...)**.

**print**     : A boolean value **(TRUE/FALSE)**.  This provide an option for users to print result.

**options**     : Options takes 1, 2 or 3 as an argument **(options =1, 2, 3)**.  This provide additional output.

\vspace{6pt}
The full syntax usage:
```{r echo=TRUE}
data1 <- c(4,5,6,5,6,5,6,4,6,5,6,4,5,4,5,6)
ctapply(data1, np=TRUE, print=TRUE, options = 3)
ctbarplot(electricdata$cost)
```
\vspace{6pt}
**Who should use this package**
```{r echo=FALSE}
cat("\n")
```
Why use **ctapply**? Use **ctapply** to quickly summarize data and identify what looks normal and what looks odd. The distribution of a variable shows what values the variable takes and how often the variable takes these values.

\vspace{6pt}

Analytics in a true sense is leveraged only through visualizations. R, as a statistical tool, offers strong visualization capabilities. So, the numerous options associated with charts is what makes them special. Each of the charts has its own application and the chart should be studied prior to applying it to a problem.





