---
title: "ctapply - An R package to measure central tendency and spread"
author: "Anthony McCofie - anthonymccofie@usf.edu"
date: "April 10, 2022"
output:
  pdf_document: 
    number_sections: true
---

ctapply: **Object Summaries**

**Description:**

**ctapply** is a package used to produce summaries of basic statistics, such as central tendency(mean, median..) and standard deviation (spread). 
The package calls specific methods to produce the result.  The user have option to print the result.


The sample data used for this package: **Cost Function of Electricity Producers (1955)**

Below are the fields for the sample data used for the package
```{r echo=FALSE}
library(ctapply)
head(electricdata)
```

**Usage:**

* You can use the package in two ways:
  + Either with the data that comes with the package **electricdata** as shown below  
  ```{r setup, warning=FALSE, message=FALSE}
  ctapply(electricdata$fuel)
  ```
  + Or use your own data such as creating a numeric vector shown below:
  ```{r warning=FALSE, message=FALSE}
  data1 <- c(4,5,6,5,6,5,6,4,6,5,6,4,5,4,5,6)
  ctapply(data1)
  ```
\newpage

**Arguments**

**object**    : An object for which a summary is desired. This could be a numeric vector or a data frame dataset

**np**        : The central tendency/spread method **(Mean, Median and ST)** to use

**print**     : A boolean value **(TRUE/FALSE)**.  This provide an option for users to print result

\vspace{6pt}
The full usage syntax is:
```{r echo=TRUE}
data1 <- c(4,5,6,5,6,5,6,4,6,5,6,4,5,4,5,6)
ctapply(data1, np=TRUE, print=FALSE)
```




